Language-Based Low-Level MPC Security: $\metaprot$ to $\minifed$

### 2024-05-10 ppdp24/bruteforce.tex
checkpoint

We can then query representations of $\runs(\prog)$ with
implementations of conditioning and marginalization to automatically
verify the passive model hyperproperties described in Section
\ref{section-hyper}-- in particular correctness and noninterference
modulo output, which imply passive security.  We have used this method
to verify security in $\mathbb{F}_2$ of Shamir addition as defined in Section
\ref{section-lang-example}, and single-gate $\eand$ and $\exor$ circuits with GMW
Beaver triples. We have also
verified properties compositional properties of gates themselves that establish
circuit invariants that imply passive security in larger circuits.
We discuss these examples and proof methods in Section \ref{section-examples}.

>>>>

\paragraph{Verifying Security Properties} We can
query correct representations of $\runs(\prog)$ by using
implementations of conditioning and marginalization to automatically
verify the passive model hyperproperties described in Section
\ref{section-hyper}-- in particular correctness and noninterference
modulo output, which imply passive security.  We have used this method
to verify security in $\mathbb{F}_2$ of Shamir addition as defined in Section
\ref{section-lang-example}, and single-gate $\eand$ and $\exor$ circuits with GMW
Beaver triples. We have also
verified properties compositional properties of gates themselves that establish
circuit invariants that imply passive security in larger circuits.
We discuss these examples and proof methods in Section
\ref{section-examples}.

### 2024-05-10 ppdp24/examples.tex
checkpoint

For full details of the GMW protocol the reader is referred to
\cite{evans2018pragmatic}. Our implementation libary is shown in
Figure \ref{fig-gmw}, with type signatures for the library functions
also shown. We present the And gate since it is
an interesting component. The Figure includes the
following top-level functions:
\begin{itemize}
\item \ttt{encodegmw}: This function encodes client 1's and client 2's
  secret bits called $\ttt{s[1,"s1"]}$ and $\ttt{s[1,"s2"]}$ into two
  distinct wire values (pairs of shares).
\item \ttt{andgmw}: This function defines the gate $\ttt{"g"}$, the
  identifier $\ttt{"g"}$ being used to distinguish randomness used
  within.  In our version client 1 builds the output table (using
  \ttt{andtablegmw})and transfers the correct output share to client 2
  using 1-out-of-4 OT ($\ttt{OT4}$), definable using $\ttt{OT}$, as
  per standard GMW protocol.
\item \ttt{decode}: This function decodes and publishes a wire value
  by $\ttt{xor}$ing the shares. Note that this requires both client 1
  and 2 to publicize their shares.
\end{itemize}
\begin{example}
  \label{example-gmw-andcircuit}
The following program uses our GMW library to define
a circuit with a single And gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively:
$$
\mathtt{decode(andgmw("gate0",encodegmw("s1"),encodegmw("s2")))}
$$
\end{example}

>>>>

For full details of the GMW protocol the reader is referred to
\cite{evans2018pragmatic}. Our implementation libary is shown in
Figure \ref{fig-gmw}, with type signatures for the library functions
also shown. We present the And gate since it is
an interesting component. The Figure includes the
following top-level functions:
\begin{itemize}
\item \ttt{encodegmw}: This function encodes client 1's and client 2's
  secret bits called $\ttt{s[1,"s1"]}$ and $\ttt{s[1,"s2"]}$ into two
  distinct wire values (pairs of shares).
\item \ttt{andgmw}: This function defines the gate $\ttt{"g"}$, the
  identifier $\ttt{"g"}$ being used to distinguish randomness used
  within.  In our version client 1 builds the output table (using
  \ttt{andtablegmw})and transfers the correct output share to client 2
  using 1-out-of-4 OT ($\ttt{OT4}$), definable using $\ttt{OT}$, as
  per standard GMW protocol.
\item \ttt{decode}: This function decodes and publishes a wire value
  by $\ttt{xor}$ing the shares. Note that this requires both client 1
  and 2 to publicize their shares.
\end{itemize}
\begin{example}
  \label{example-gmw-andcircuit}
The following program uses our GMW library to define
a circuit with a single And gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively:
\begin{verbatimtab}
decode(andgmw("gate0",encodegmw("s1"),encodegmw("s2")))
\end{verbatimtab}
\end{example}

\begin{lemma}
  Given:
  $$
  (\varnothing,\andgmw(xy,\mesg{x},\mesg{y}) \redx (\prog,\mesg{xy})
  $$
  Then for all
  $$
  \store \in \mems(\{ \elab{\secret{y}}{2}, \out{1} \} \cup \iov(\prog))
  $$
  such that
  \begin{mathpar}
    %\store(\elab{\secret{x}}{1}) = \elab{\mesg{x}}{1} + \elab{\mesg{x}}{2}
    %
    \store(\elab{\secret{y}}{2}) = \cod{\store, \elab{\mesg{y}}{1} + \elab{\mesg{y}}{2}}

    \store(\out{1}) = \cod{\store, \elab{\mesg{xy}}{1} + \elab{\mesg{xy}}{2}}
  \end{mathpar}
  we have:
  $$
  \progtt(\prog)(\elab{\mesg{x}}{1} + \elab{\mesg{x}}{2}|\store_{\{ \secret{y}{2}, \out{1} \}}) =
  \progtt(\prog)(\elab{\mesg{x}}{1} + \elab{\mesg{x}}{2}|\store)
  $$
\end{lemma}

### 2024-05-10 ppdp24/gmw.tex
checkpoint

\begin{fpfig}[t]{2-Party GMW circuit library with And gate.}{fig-gmw}
{\footnotesize
  \begin{verbatimtab}
    encodegmw(in, i1, i2) {
      m[in]@i2 := (s[in] xor r[in])@i2;
      m[in]@i1 := r[in1]@2;
      m[in]
    }

    andtablegmw(b1, b2, r) {
      let r11 = r xor (b1 xor true) and (b2 xor true) in
      let r10 = r xor (b1 xor true) and (b2 xor false) in
      let r01 = r xor (b1 xor false) and (b2 xor true) in
      let r00 = r xor (bl xor false) and (b2 xor false) in
      { v1 = r11; v2 = r10; v3 = r01; v4 = r00 }
    }

    andgmw(g, v1, v2) {
      let r = r[g] in
      let table = andtablegmw(v1,v2,r) in
      m[g]@2 := OT4(v1,v2,table,2,1);
      m[g]@1 := r;
      m[g]
    }

    decodegmw(v) {
      p[1] := v@1; p[2] := v@2;
      out@1 := (p[1] + [2])@1;
      out@2 :=(p[1] + [2])@2
    }
  \end{verbatimtab}
}
\end{fpfig}

>>>>

\begin{fpfig}[t]{2-Party GMW circuit library with And gate.}{fig-gmw}
{\footnotesize
  \begin{verbatimtab}
    encodegmw(in, i1, i2) {
      m[in]@i2 := (s[in] xor r[in])@i2;
      m[in]@i1 := r[in]@2;
      m[in]
    }

    andtablegmw(b1, b2, r) {
      let r11 = r xor (b1 xor true) and (b2 xor true) in
      let r10 = r xor (b1 xor true) and (b2 xor false) in
      let r01 = r xor (b1 xor false) and (b2 xor true) in
      let r00 = r xor (bl xor false) and (b2 xor false) in
      { row1 = r11; row2 = r10; row3 = r01; row4 = r00 }
    }

    andgmw(g, v1, v2) {
      let r = r[g] in
      let table = andtablegmw(v1,v2,r) in
      m[g]@2 := OT4(v1,v2,table,2,1);
      m[g]@1 := r@1;
      m[g]
    }

    decodegmw(v) {
      p["1"] := v@1; p["2"] := v@2;
      out@1 := (p["1"] + p["2"])@1;
      out@2 := (p["1"] + p["2"])@2
    }
  \end{verbatimtab}
}
\end{fpfig}
